My title

### 2024-11-14 paper/paper.qmd
update paper

#### Load libraries ####
library(tidyverse)
library(rstanarm)

#### Read data ####
data <- read.csv("data/02-analysis_data/analysis_data.csv")

#### Load the saved model ####
first_model <- readRDS("models/Mortality_Model.rds")

#### Create predictions based on model ####
# Get predictions and add them to the dataset
analysis_data <- data %>%
  mutate(predicted_mortality = posterior_predict(first_model) %>% apply(2, mean))

#### Plot Mortality vs Food ####
plot_food <- ggplot(analysis_data, aes(x = Food, y = Mortality)) +
  geom_point(color = "blue", alpha = 0.6) +
  geom_line(aes(y = predicted_mortality), color = "red", size = 1) +
  labs(title = "Mortality vs Food", x = "Food", y = "Mortality")

#### Plot Mortality vs Health Expense ####
plot_health_expense <- ggplot(analysis_data, aes(x = Health_expense, y = Mortality)) +
  geom_point(color = "blue", alpha = 0.6) +
  geom_line(aes(y = predicted_mortality), color = "red", size = 1) +
  labs(title = "Mortality vs Health Expense", x = "Health Expense", y = "Mortality")

#### Plot Mortality vs Vaccine ####
plot_vaccine <- ggplot(analysis_data, aes(x = Vacinne, y = Mortality)) +
  geom_point(color = "blue", alpha = 0.6) +
  geom_line(aes(y = predicted_mortality), color = "red", size = 1) +
  labs(title = "Mortality vs Vaccine", x = "Vaccine", y = "Mortality")

#### Save the plots ####
ggsave("plots/mortality_vs_food.png", plot = plot_food, width = 8, height = 6)
ggsave("plots/mortality_vs_health_expense.png", plot = plot_health_expense, width = 8, height = 6)
ggsave("plots/mortality_vs_vaccine.png", plot = plot_vaccine, width = 8, height = 6)

>>>>

#### Load libraries ####
library(tidyverse)
library(rstanarm)
library(knitr)

#### Read data ####
data <- read_csv(file = here::here("data/02-analysis_data/analysis_data.csv"))

#### Load the saved model ####
first_model <- readRDS(file = here::here("models/Mortality_Model.rds"))
summary_table <- summary(first_model)

# Display the summary in a formatted table
kable(summary_table, digits = 2, caption = "Summary of Mortality Model")
